\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-18 draft.tex
paste intro/conclusion material from presentation into draft

@@

@@

After this, uncertainty about the government agency's preferences is resolved. All players simultaneously observe the realization of the random variable $\ta$ that represents this uncertainty. The political stage concludes with the agency making a choice to renew the antidumping duties or let them expire. In the event that the antidumping duties expire, the home country's trade policy reverts to the trade agreement tariff $\tau^a$. Finally, producers and consumers make their decisions.

@@

>>>>

\begin{enumerate}
	\item How long do deviations from trade agreement tariffs last? 
  \item What are the determinants of renewals?
		\begin{itemize}
			\item They don't happen for \textit{no} reason at all
		\end{itemize}
\end{enumerate}

\vskip.2in
\begin{itemize}
	\item Temporary trade barriers have potential to be renewed
		\begin{itemize}
			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
			\item For Safeguards, four then four; much rarer than AD
		\end{itemize}
	\item Authorized by WTO
	\item Very little in the agreements to guide the process
		\begin{itemize}
			\item WTO litigation gives gov'ts a LOT of latitude
			\item Renewal decision determined by complex process including DOC, ITC, pressure via other political bodies.
		\end{itemize}
	\item In U.S., for AD:
		\begin{itemize}
			\item DOC initiates, determines whether dumping would continue
						\begin{itemize}
			\item Can renew AD duties
			\item Susceptible to influence of lobbying, perhaps both direct and indirect
			\item Modeled in reduced form
		\end{itemize}

			\item ITC determines whether injury would recur / continue
		\end{itemize}
\end{itemize}

\vskip.2in
The probability that an AD duty gets renewed

\begin{itemize}
	\item Increases in lobbying effort
	\item Decreases in the MFN tariff
	\item Is invariant to the trading partner's tariff
	\item Increases in the profitability of the import-competing sector
	\item Increases in the strength of the lobby
	\item May be concave in the AD duty
\end{itemize}

@@

Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)

@@

After this, uncertainty about the government agency's preferences is resolved.

Lobby must be able to trigger the original AD duty
\begin{itemize}
	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
	\item It could be justified, not motivated by politics/rent-seeking
	\item But still, firms lobby for duties they don't get
\end{itemize}

\vskip.1in
So what's the uncertainty about?

\begin{itemize}
	\item Strength of evidence
	\item Probability foreign will retaliate or initiate dispute (indirect)
	\item $G$'s valuation of harm to industry, e.g. how politically important is industry?
	\item Uncertainty could be, in part, about how mobile labor is (Kishore)
\end{itemize}

All players simultaneously observe the realization of the random variable $\ta$ that represents this uncertainty. The political stage concludes with the agency making a choice to renew the antidumping duties or let them expire. In the event that the antidumping duties expire, the home country's trade policy reverts to the trade agreement tariff $\tau^a$. Finally, producers and consumers make their decisions.

@@

			Future Work

\begin{itemize}
	\item Comparative static on uncertainty measure
	\item Empirical work
	\item Extend model to include initial decision to grant protection.
		\begin{itemize}
			\item Explain variation in a lobby's incentives between original application of AD and renewal
			\item Lobby's choice between investing in productive vs. rent-seeking behavior while protected
			\item Need to have first stage (Jee-Hyeong, Gary Lyn)
		\begin{itemize}
			\item Look at Park and Blonigen (Jee-Hyeong)
			\item Cost differential for firms to get initial duty vs. renewal?
			\item Some firms choose not to pursue renewal when DOC contacts them 30-days before (Sasha)
		\end{itemize}
	\item Lobbying effort may be endogenous: if prob. of success is lower, maybe it's not worth providing effort (Mostafa)
		\end{itemize}
\end{itemize}
